Responses to the Reviewers' Comments

### 2024-11-04 Response/Paper_Res.tex
Rev_V8.3

\section{Related Work}
\label{section:II}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment.

	%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
	%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
	%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}

	%, while uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges in MEC systems with limited resources.

	\textcolor{blue}{In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.}

	\textcolor{blue}{\subsection{DRL-based Computation Offloading for MEC}
		To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
		Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
		Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. 
		Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
		These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
		Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios.}

	\textcolor{blue}{Some studies explored task offloading problems in more advanced scenarios. Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
		To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent deep Q-network (DQN)-based algorithm.
		Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to concurrently optimize resource allocation and computation offloading.
		In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
		These works did not take into account the challenges of a dynamic network environment. For instance, in \cite{chen2021drl}, MDs are assumed to have sufficient transmission and computation resources from ENs, which may not always align with real-world conditions. While the works of \cite{wu2024privacy}--\cite{zhao2019deep} investigated the limited resources in MEC, they did not consider the dynamic workload at ENs in decision making processes, imposing significant challenges in overall system performance. } 
	\textcolor{blue}{\subsection{Queuing Theory for Efficient Resources Scheduling}}
	%In fact, the state of MD's computing and transmission power, arrived task's requirement, the energy state of MDs, and workloads at ENs all change dynamically with time in actual systems, 
	%On the other hand, although the works [11]–[15] considered non-divisible tasks, they do not take into account the underlying queuing systems. As a result, the processing and transmission of each task should always be accomplished within one time slot (or before the arrival of the next task), which may not always be guaranteed in practice.

	\textcolor{blue}{To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.
		To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
		Liao \textit{et al.} in \cite{liao2023online} introduced a double DQN (DDQN)-based algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
		To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.
		In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. 
		Huang \textit{et al.} in \cite{huang2021deadline} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks.
		In above research \cite{munir2021multi}--\cite{huang2021deadline}, while queuing models were employed in several parts of the system, the offloading process was not approached as a holistic queuing system. }

	\textcolor{blue}{\subsection{Task Offloading Considering EN's Workload}
		Due to the limited processing capacities of ENs, the processing capacity that an EN allocates to an MD depends on the EN's workload each time. Treating this dynamic workload as part of the environment can negatively impact system performance and requires careful consideration. Specifically, offloaded tasks may experience significant processing delays or be dropped if their deadlines expire. Some existing works have addressed the load levels at the edge nodes and proposed task offloading algorithms.
		Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the IIoT systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
		To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.
		Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
		Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
		In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.
		However, these algorithms in \cite{gong2022edge}–\cite{gao2022large} require global information of the system and may incur high signaling overhead.}

	%Other works have proposed distributed task offloading algorithms considering the load levels at the edge nodes, where each mobile device makes its offloading decision in a decentralized manner.

	%Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly. In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands.

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{enumerate}[]
\item We have devoted Section II of the revised manuscript to the literature review and provided a survey of the recently published state-of-the-art works.
\item Furthemore, we have expanded the explanations about each related work and discussed its pros/cons.
\end{enumerate}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. We have also included a table to provide a comprehensive comparison of the related works. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

\,\,\,\, Some studies explored task offloading problems in more advanced scenarios. Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent deep Q-network (DQN)-based algorithm.
Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to concurrently optimize resource allocation and computation offloading.
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
These works did not take into account the challenges of a dynamic network environment. For instance, in \cite{chen2021drl}, MDs are assumed to have sufficient transmission and computation resources from ENs, which may not always align with real-world conditions. While the works of \cite{wu2024privacy}--\cite{zhao2019deep} investigated the limited resources in MEC, they did not consider the dynamic workload at ENs in decision making processes, imposing significant challenges in overall system performance.
\subsection{Queuing Theory for Efficient Resources Scheduling}
\,\,\,\,To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.
To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 

@@

To investigate privacy aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} proposed a DQN-based method. They transform the problem on MDP to optimize computation rate and energy consumption in a queuing-based IIoT network.
In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. 

@@

In above research \cite{munir2021multi}--\cite{huang2021deadline}, while queuing models were employed in several parts of the system, the offloading process was not approached as a holistic queuing system. 
\subsection{Task Offloading Considering EN's Workload}
\,\,\,\,Due to the limited processing capacities of ENs, the processing capacity that an EN allocates to an MD depends on the EN's workload each time. Treating this dynamic workload as part of the environment can negatively impact system performance and requires careful consideration. Specifically, offloaded tasks may experience significant processing delays or be dropped if their deadlines expire. Some existing works have addressed the load levels at the edge nodes and proposed task offloading algorithms.
Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT (IIoT) systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
To optimize delay and energy consumption in an MEC-based IIoT system, Wu \textit{et al.} in \cite{wu2023multi} proposed a multi-agent DQN-based method based on POMDP to address computation offloading problem.
Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.

@@

However, these algorithms in \cite{gong2022edge}–\cite{gao2022large} require global information of the system and may incur high signaling overhead.}

>>>>

	\section{Related Work}
	\label{section:II}
		In recent years, numerous studies have focused on computation offloading in MEC, covering a broad range of applications, including IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive}. 
		To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of DRL in adapting to environmental changes and learning optimal strategies. In this section, we explore the current DRL-based state-of-the-art works and discuss their strengths and limitations. Table~\ref{table1} provides an intuitive comparison of these works.
		\subsection{DRL-based Optimization Methods for MEC}

		There are two primary categories of related research in resource management for MEC based on target objectives, single-objective optimization and multi-objective optimization methods, where RL are mainstream optimization techniques.
		\subsubsection{Single-Objective Optimization} 
		Recent research has extensively explored single-objective optimization in the context of MEC, focusing on optimizing a single objective, such as delay or energy consumption. 
		Given the dynamic nature of MEC systems, in \cite{li2022integrated} the authors proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control. 
		Li \textit{et al.} in \cite{li2020joint} introduced a DRL-based delay-optimal offloading strategy that employs a DQN to learn offloading decisions autonomously. 
		To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
		Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
		To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
		Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
		Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility. 
		In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
		Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently.

		\subsubsection{Multi-Objective Optimization.}

		In MEC environments, multiple objectives often compete, requiring a balance in decision-making. For instance, task offloading must carefully navigate trade-offs between delay and energy consumption, as well as balance energy usage against the number of completed tasks. Research has increasingly addressed these multi-objective optimization challenges.
		Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
		To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DQN-based algorithm. 
		Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. 
		Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
		Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. 
		In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation.

		To further enhance the modeling of real-world scenarios, some studies have applied queuing theory to model MEC systems, which helps capture the dynamic nature of the network and allows MEC systems to allocate computational and transmission resources more efficiently.
		Liao \textit{et al.} in \cite{liao2023online} introduced a double DQN (DDQN)-based algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
		To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.
		Huang \textit{et al.} in \cite{huang2021deadline} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. 
		Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
		Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the IIoT systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
		To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.
		In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.

		\subsection{Analysis and Motivation}
		Despite extensive research efforts, task offloading continues to encounter significant challenges in real-world scenarios involving multiple MDs and ENs. We discuss these challenges from two aspects, i.e., system modeling and target objective optimization.

		\subsubsection{System modeling}

		Some existing works primarily focus on simplified MEC networks, investigating single MEC network models. For instance, studies \cite{zhou2021deep}, \cite{liu2021learn} only examine single-server or single-user scenarios, while \cite{huang2019deep}--\cite{wu2023computation} do not account for delay-sensitive tasks. In contrast, our research addresses a more realistic MEC scenario, considering delay-sensitive tasks with processing deadlines. This is challenging due to the interplay between processing deadlines, load dynamics at the ENs, and the resulting offloaded task delays. Additionally, the absence of robust underlying resource scheduling systems can lead to data congestion during transmission and inefficient resource allocation, hindering overall system performance \cite{wang2020reinforcement}--\cite{chen2021drl}. Hence, more accurate MEC models are necessary to handle the complexities of dynamic resource scheduling in large-scale scenarios.
		To better represent real-world scenarios, authors in \cite{Bolourian-WCL24}--\cite{9253665} have applied queuing theory to model MEC systems. This approach helps capture the dynamic nature of networks, enabling MEC systems to allocate computational and transmission resources more efficiently. In a similar vein, we approached the offloading process as a holistic queuing system, where multiple queues ensure fair resource scheduling for MEC, leading to more accurate and efficient resource management.

		In addition, the limited processing capacities of ENs necessitate careful consideration when allocating resources to MDs. The processing capacity allocated to an MD depends on the dynamic workload of an EN at any given time. Some studies have failed to account for these challenges in dynamic network environments, resulting in reduced system performance. For example, in \cite{chen2021drl}, it is assumed that MDs have sufficient transmission and computation resources from ENs, which may not reflect real-world conditions. While the works \cite{zhao2019deep}, \cite{dai2020edge}, and \cite{wu2024privacy} investigated limited resources in MEC, they did not consider dynamic workloads at ENs in decision-making processes, leading to potential performance issues.
		Certain studies such as \cite{sun2024hierarchical}, \cite{gong2022edge}-\cite{gao2022large} have addressed load levels at ENs and proposed task offloading algorithms. However, these algorithms often require global system information, resulting in high signaling overhead. In contrast to these works, we propose a distributed algorithm that effectively manages unknown load dynamics at ENs. This algorithm enables each MD to make offloading decisions independently, without requiring information (e.g., task models, offloading decisions) from other MDs, thereby reducing signaling overhead and improving overall system performance.

		\subsubsection{Optimization Objectives}
		Considering delay and energy consumption as optimization objectives represents a significant research focus in MEC. Most existing studies tend to optimize these two objectives independently, often neglecting the conflicts that arise between them, which can lead to skewed optimization results. Additionally, some research has prioritized maximizing the number of completed tasks, highlighting the advantages that MEC systems offer. Therefore, delay, energy consumption, and the number of completed tasks are critical factors in the design of MEC systems. However, to the best of our knowledge, there has been limited research that simultaneously addresses all three objectives.
		Different from works \cite{li2022integrated}-\cite{dai2020edge}, which only focus on delay-optimal optimization or energy-efficient optimization, we are motivated to emphasize the MEC system with delay, energy consumption, and the number of completed tasks as three objectives for QoE optimization. Multi-objective studies \cite{chen2021drl}-\cite{gao2022large} have mostly investigated the trade-off between two or three of these factors but fail to properly address user demands and fulfill QoE requirements. QoE is a time-varying performance measure that reflects user satisfaction, where each user may have unique QoE requirements according to the Mobile Devices' (MDs) individual preferences.
		In contrast to \cite{li2022integrated}-\cite{gao2022large}, to effectively address personalized QoE optimization, we define an adaptive trade-off between task completion and cost reduction. We introduce a weighted sum between completion delay and energy consumption as an associated cost. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes. \color{black}

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{enumerate}[]
\item We have devoted Section II of the revised manuscript to the literature review and provided a survey of the recently published state-of-the-art works.
\item Furthemore, we have expanded the explanations about each related work and discussed its pros/cons.
\end{enumerate}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. We have also included a table to provide a comprehensive comparison of the related works. 
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
		\section{Related Work}
		\label{section:II}

		\,\,\,\,
		In recent years, numerous studies have focused on computation offloading in MEC, covering a broad range of applications, including IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive}. 
		To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of DRL in adapting to environmental changes and learning optimal strategies. In this section, we explore the current DRL-based state-of-the-art works and discuss their strengths and limitations. Table~\ref{table1} provides an intuitive comparison of these works.
		\subsection{DRL-based Optimization Methods for MEC}

		\,\,\,\,
		There are two primary categories of related research in resource management for MEC based on target objectives, single-objective optimization and multi-objective optimization methods, where RL are mainstream optimization techniques.\vspace{3mm}
		\subsubsection{Single-Objective Optimization} 
		Recent research has extensively explored single-objective optimization in the context of MEC, focusing on optimizing a single objective, such as delay or energy consumption. 
		Given the dynamic nature of MEC systems, in \cite{li2022integrated} the authors proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control. 
		Li \textit{et al.} in \cite{li2020joint} introduced a DRL-based delay-optimal offloading strategy that employs a DQN to learn offloading decisions autonomously. 
		To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
		Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
		To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
		Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
		Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility. 
		In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
		Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently.\vspace{3mm}

		\subsubsection{Multi-Objective Optimization.}
		In MEC environments, multiple objectives often compete, requiring a balance in decision-making. For instance, task offloading must carefully navigate trade-offs between delay and energy consumption, as well as balance energy usage against the number of completed tasks. Research has increasingly addressed these multi-objective optimization challenges.
		Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
		To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DQN-based algorithm. 
		Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. 
		Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
		Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. 
		In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. \vspace{3mm}

		\,\,\,\,
		To further enhance the modeling of real-world scenarios, some studies have applied queuing theory to model MEC systems, which helps capture the dynamic nature of the network and allows MEC systems to allocate computational and transmission resources more efficiently.

@@

		To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.

@@

@@

		\begin{table*}[tbp]\textcolor{blue}{
				\renewcommand{\arraystretch}{0.2}
				\captionsetup{name=TABLE}
				\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
				\scalebox{0.7}{%
					\begin{tabular}{ lp{7cm}p{6cm}p{4cm}p{6cm}l} 
						\toprule
						\textbf{Paper}  &  \textbf{Problem} &  \textbf{Objective} & \textbf{Method} &  \textbf{Limitation}  \\ \midrule
						\cite{li2022integrated} & Online computation offloading & Minimize computation delay & Actor-critic network & Not consider system energy consumtion \\ \midrule
						\cite{li2020joint} & Caching and computation offloading & Minimize delay of the whole system &  Multi-agent DQN & Not consider system energy consumtion \\ \midrule
						\cite{tang2022double}  & Computation offloading & Minimize total delay & DDQN & Not consider system energy consumtion \\ \midrule
						\cite{wang2020reinforcement} & Mobility aware computation offloading & Minimize energy consumtion & Q-learning & Not consider computation delay\\ \midrule
						\cite{liu2021learn}  & Resource allocation and computation offloading & Minimize execution cost  & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
						\cite{wu2023computation}   & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
						\cite{zhou2021deep} & Resource allocation and computation offloading & Minimize energy consumption of the entire system & DDQN & Only for a single MEC system model \\\midrule				
						%\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
						\cite{wu2024privacy} & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service.  & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
						\cite{dai2020edge} & Resource allocation and computation offloading & Minimize energy consumption & DDPG & Not take user's demand into consideration \\\midrule
						\cite{zhao2019deep} & User association and resource allocation & Optimize downlink utility  & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
						\cite{liao2023online}  & Online computation offloading & Minimize computation delay and energy consumption & DDQN & Only for a single MEC system model  \\\midrule
						\cite{wu2024combining}   & Privacy aware computation offloading & Optimization of computation rate and energy consumption  & Actor-critic network  & Not take user's demand into consideration \\\midrule
						\cite{Bolourian-WCL24}  & Energy harvesting  computation offloading & Minimize drop rate and energy consumption.  & DQN & Not consider computation delay  \\\midrule
						\cite{huang2021deadline}  & Computation offloading & Optimize drop rate and energy consumption & DDPG & Not consider computation delay \\ \midrule
						\cite{gong2022edge} & Resource allocation and computation offloading & Minimize task computation delay and energy consumption  & DRL & Not take user's demand into consideration\\\midrule
						\cite{sun2024hierarchical} & Computation offloading and service caching & Minimize average service delay & Hierarchical DRL & Not consider system energy consumtion \\\midrule
						\cite{wu2023multi}  & Computation offloading & Optimize delay and energy consumption  & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
						\cite{9253665}  &  Computation offloading & Minimize drop rate and computation delay.  & D3QN + LSTM & Not consider system energy consumtion\\\midrule
						\cite{gao2022large}  & Decentralized computation offloading & Optimize system cost and completion rates  & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
						QECO  &  Computation offloading & Maximize the QoE of each MD individually & D3QN + LSTM & \\
						\toprule
				\end{tabular}}
				\label{table1}}
		\end{table*}
		\subsection{Analysis and Motivation}
		\,\,\,\,
		Despite extensive research efforts, task offloading continues to encounter significant challenges in real-world scenarios involving multiple MDs and ENs. We discuss these challenges from two aspects, i.e., system modeling and target objective optimization. \vspace{3mm}
